---
---
title: "function"
author: "Messan kodzo AKOTIA"
date: "2024-05-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#load packages\*\*\*\*

```{r cars}
if (!require(pacman)) install.packages("pacman")
pacman::p_load(tidyverse, dplyr,here, NHSRdatasets, medicaldata, outbreaks,
reactable)

```

## create your own function to Function to convert age in years to age in months

```{r}
years_to_months <- function(age_years) {
  age_months <- age_years * 12
  return(age_months)
}
```

# create your own function fahrenheit_to_celsuis

```{r}
fahrenheit_to_celsius <- function(fahrenheit) {
celsius <- (5 / 9) * (fahrenheit - 32)
return(celsius)
}
fahrenheit_to_celsius(32)
```

# apply my function
```{r}
airquality %>%
select(Temp) %>%
mutate(Temp = fahrenheit_to_celsius(Temp)) %>%
head()
```

#create your own functioncelsuis_to_fahrenheit

```{r}
# Function to convert temperature from Celsius to Fahrenheit
celsius_to_fahrenheit <- function(temperature_celsius) {
  temperature_fahrenheit <- temperature_celsius * 1.8 + 32
  return(temperature_fahrenheit)
}
```

#test our own function

```{r}
library(datasets)
beaver1 %>%
select(temp) %>%mutate(temp = celsius_to_fahrenheit(temp))%>%
  head()
```

# functions with Multiples arguments

```{r}
calc_bmi <- function(weight_kg, Height) { Height_m <- Height/100
  bmi <- weight_kg / (Height_m^2)
  return(bmi)
}
```

#apply my function
```{r}
medicaldata::smartpill %>%
as_tibble() %>%
select(Weight, Height) %>%
mutate(BMI = calc_bmi(Weight, Height))
```

## practice with Calculate calories

```{r}
calculate_calories <- function(carb_grams = 0, protein_grams = 0, fat_grams = 0) {
  result <- (carb_grams * 4) + (protein_grams * 4) + (fat_grams * 9)
 result_rounded <- round(result, 2)
  return(result_rounded)
}

```

## an example

```{r}
calculate_calories(carb_grams = 50.45, protein_grams = 20.67, fat_grams = 10.9087)

```

# practices to celsius_ convert
```{r}
celsius_convert <- function(temp, unit) {
  if (unit == "celsius") {
    return(temp)
  } else if (unit == "fahrenheit") {
    return((temp - 32) / 1.8)
  } else {
    stop("Invalid unit provided. Please use 'celsius' or 'fahrenheit'.")
  }
}
```

#checking error

```{r}
print(celsius_convert(20, "celsius")) 
print(celsius_convert(68, "fahrenheit")) 
```

##correct function
```{r}
check_negatives <- function(numbers) {
  if (any(numbers < 0)) {
    print("x contient des nombres négatifs")
  } else {
    print("x ne contient pas de nombres négatifs")
  }
}
```

#check functionnality of the function cheeck_negatives
```{r}
test1<- check_negatives(c(8, 3, -2, 5)) 
test2<- check_negatives(c(10, 20, 30, 40))
```
#Argument validityChecking with Conditionals
```{r}
calculate_calories2 <- function(carb_grams = 0, protein_grams = 0, fat_grams = 0) {
  if (!is.numeric(carb_grams) || !is.numeric(protein_grams) || !is.numeric(fat_grams)) {
    stop("All input arguments must be numeric.")
  }
  result <- (carb_grams * 4) + (protein_grams * 4) + (fat_grams * 9)
  
  return(result)
}
print(calculate_calories2(30, 20, 10))

#create and check error
print(calculate_calories2(30,"20", 10))

```


# Vectorized Conditionals
```{r}
calculate_isoniazid_dosage2 <- function(weight) {
  if (any(weight < 30)) stop("Weights must all be at least 30 kg.")
  
  # Calculer le dosage en fonction du poids
  out <- ifelse(weight <= 35, 150,
           ifelse(weight <= 45, 200,
             ifelse(weight <= 55, 300,
               ifelse(weight <= 70, 300, 300))))
  
  return(out)
}

# checking function
calculate_isoniazid_dosage2(c(30, 40, 50, 100))

```

```{r}

```

